---
title: "Proteome-wide Screen for RNA-dependent Proteins in Non-Synchronized
  HeLa cells"
author: "Alisa Kirkin, Sina Kühnel, Ignacio Lozano Onrubia, Greta Pick"
date: "19/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Final Report

Idee: vielleicht keine 1-bla Nummerierung, sondern Aufteilung in Phase 1-5 und dann Unterpunkte mit Header2

# 1. Introduction
What are RNA-binding and RNA-dependent proteins?
Why important? 

## 1.1 Brief summary of experiment
Include picture of experiment.

## 1.2 Goals
Automatic dentification of RNA-dependent proteins based on fraction shift.

# 2. Description of the Dataset
Control and RNase group

# 3. Data Clean Up and Normalization 
Clean Up is needed to...
Split of Control and RNase group. 
Maybe even more subtables?


# 3.1 Data Clean Up
No missing values -> summary function
Removing of all 0 rows.

## 3.2 Normalization 
Why needed?
Include picture to illustrate method.
Normalization factor... Describe method.
Show barplot before and after. Maybe even distribution.

## 3.3 Scaling
Why needed?
Include formula. 

# 4. Maxima and Gaussian Curve 

## 4.1 Smoothing the Curve


## 4.2 Identification of global Maxima


## 4.3 Gauss fitting to the Curve











```{r pressure, echo=FALSE}

```


